CA of Music Genre Stereotypes

### 2025-06-20 analysis-bb-new.qmd
whateves

```{r Creating individual matrices}
   make.mat <- function(x) {
      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
      return(x)
      }
   bb.sdsm <- function(x) {
     tryCatch({
         w <- sdsm(x, alpha = 0.25, narrative = FALSE)
         return(w)
            }, error = function(e) {return(NULL)})
      }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .9 | den < 0.1)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, make.mat) # creating individual two mode network of genre by labels
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
   row.bb <- lapply(ind.mat, bb.sdsm)
   col.bb <- lapply(ind.mat.t, bb.sdsm)
   null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
   null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
   row.bb <- row.bb[-null.rows]
   col.bb <- col.bb[-null.cols]
   row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(col.bb), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   m <- nrow(row.stack)/20
   rownames(row.stack) <- rep(r, m) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, m) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
```

@@

```{r Genre Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "genre-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat, 
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 3, b = 3, l = 2, r = 3,
                     c("Rap", "Folk", "Classical"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3,
                     c("Alt_Rock", "Gospel", "Opera"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 5,
                     c("Metal", "Bluegrass", "Broadway"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex4.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Jazz", "Reggae", "Blues", "Rap", "Classical"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex5.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Country", "Bluegrass", "Classic_Rock", "Folk"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex6.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Alt_Rock", "Contemp_Rock", "Classic_Rock", "Metal"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex7.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 4,
                     c("Broadway", "Classical", "Opera", "Easy", "Jazz"))
   dev.off()
```

>>>>

```{r Creating individual matrices}
   make.mat <- function(x) {
      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
      return(x)
      }
   bb.sdsm <- function(x) {
     tryCatch({
         w <- sdsm(x, alpha = 0.35, narrative = FALSE)
         return(w)
            }, error = function(e) {return(NULL)})
      }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .9 | den < 0.1)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, make.mat) # creating individual two mode network of genre by labels
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
   ind.row <- lapply(ind.mat, function(x) {x %*% t(x)}) # individual genre projection
   ind.col <- lapply(ind.mat, function(x) {t(x) %*% x}) # individual label projection
   #row.bb <- lapply(ind.mat, bb.sdsm)
   #col.bb <- lapply(ind.mat.t, bb.sdsm)
   #null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
   #null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
   #row.bb <- row.bb[-null.rows]
   #col.bb <- col.bb[-null.cols]
   #save(row.bb, col.bb, file = "bb.RData")
   load(here("bb.RData"))
   row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(col.bb), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   m <- nrow(row.stack)/20
   rownames(row.stack) <- rep(r, m) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, m) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
```

@@

```{r Genre Cloud Plots}
   source(here("make.fuzz.plot.R"))
   h <- 625
   w <- 750
   png(file = here("Plots", "genre-proto-ex1.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat, 
                     seed = 125, ls = 5, 
                     1, 2, pa = .35,  t = 3, b = 3, l = 2, r = 3, bns = 6,
                     c("Rap", "Folk", "Classical"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex2.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                     c("Alt_Rock", "Gospel", "Opera"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex3.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                     c("Metal", "Bluegrass", "Broadway"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex4.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3.25, bns = 6,
                     c("Jazz", "Reggae", "Blues", "Rap", "Classical"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex5.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                     c("Country", "Bluegrass", "Classic_Rock", "Folk"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex6.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                     c("Alt_Rock", "Contemp_Rock", "Classic_Rock", "Metal"))
   dev.off()
   png(file = here("Plots", "genre-proto-ex7.png"), width=w, height=h)
      make.fuzz.plot(row.gen.dat, col.gen.dat, sup.gen.dat,
                     seed = 125, ls = 5,
                     1, 2, pa = .35,  t = 2, b = 2, l = 2, r = 3, bns = 6,
                     c("Broadway", "Classical", "Opera", "Easy", "Jazz"))
   dev.off()
```
